### 2017-01-13 MSSM/MSSM.tex
Adding something on tau iso for tt

In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of \Pgt leptons will be discussed. The results presented
here correspond to those from an analysis peformed on 12.9 fb$^{-1}$ collected
at $\sqrt{s}=13$ TeV during the first half of the 2016 p--p running period of the \ac{LHC}, 
detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
states of the di-\Pgt pair were studied. The results of this search are 
model--independent upper limits on $\sigma \times$ BR of \PHiggs or \PHiggsps 
production in the two decay modes (see THEORY) and decay into $\Pgt\Pgt$. In 
addition, the results are interpreted in MSSM benchmark scenarios and 2D likelihood
scans of the two production modes are performed. A very similar analysis
was performed on 2.3 fb$^{-1}$ of data collected at $\sqrt{s}=13$ TeV during the 2015 \ac{LHC} p--p running period. 
As it is so similar to the analysis performed on the 2016 dataset it
will not be described in detail here, more information can be found in reference \cite{CMS-PAS-HIG-16-006}.
The results of the 2015 analysis will be shown, in addition to a combination of the 2015 and 2016 datasets.

For the analysis described in this chapter, as well as the 2015 analysis not detailed
here, I was responsible for optimisation of object selection and categorisation,
as well as studies of background methods for the \mutau, \etau and \tautau channels,
evaluation of systematic uncertainties in all four channels, and for producing
the statistical results, including model--dependent interpretations.

@@

\ttbar- and single-top background samples are generated using \texttt{Powheg},
with \texttt{MadGraph5\_aMC\@NLO} \cite{amcnlo} used for the generation of di--boson background
samples and part of the W+$\gamma$ background included in the \emu channel only.
\Wjets and \Zll backgrounds are generated with the \ac{MadGraph 5} \cite{madgraph}
matrix element generator. Both samples containing a mixture
of jet multiplicities (`inclusive' samples) and samples with 1,2,3 or 4 jets (`exclusive' samples)
are generated. These exclusive samples increase the available number of
background events with higher jet multiplicities.  Part of the W+$\gamma$ background
samples are also generated with this event generator.
%note LO samples used because to get same number of effective
%events would need to generate more NLO samples
The `inclusive' and `exclusive' samples are reweighted
before they are combined so as to preserve the correct
fractions of events with each jet multiplicity.

@@

Based on this information, for the analysis on the 2015 dataset the selection was optimised
for mass points around 700-800 GeV. For the analysis on the 12.9 fb$^{-1}$ collected
in the first half of 2016, the selection was further loosened by 10 GeV in \mT~cut
and one step in hadronic tau isolation working point, to obtain the medium isolation working
point selection combined with a selection on \mT$<40$ GeV.

@@

The offline event selection continues by requiring both hadronic taus to be oppositely charged, separated
by $\Delta R > 0.5$, have pT~ of at least 40 GeV and $|\eta|<2.1$. Both taus need
to pass decay mode finding and have originated from the primary vertex, with the impact parameter $d_{z} < 0.2$ cm. 
Both taus need to pass the tight working point of the isolation discriminator, the very loose 
working point of the anti--electron discriminator and the loose working point of the anti--muon discriminator. 
The tight working point of the isolation discriminator is chosen to optimise the sensitivity
of this channel for higher masses. INSERT PLOT

@@

\section{Combination of 2015 and 2016 datasets}
\label{sec:mssm_combination}
The results outlined in the previous section, for the analysis
on a dataset corresponding to an integrated luminosity of 12.9 fb$^{-1}$
at a centre-of-mass energy of 13 TeV, collected during the 2016 running period
of the \ac{LHC}, can be combined with the results from a very similar analysis
performed on 2.3 fb$^{-1}$ collected at 13 TeV during 2015, detailed
in reference \cite{CMS-PAS-HIG-16-006}. This combination should be able
to improve slighty on the limits set by the 2016 analysis. Because the 
analysis on the 2015 dataset is very similar to the 2016 analysis it 
is not described in detail, however, the results will
be presented, and key differences with the more recent result highlighted
where needed.

\subsection{Results from 2015 analysis}
\label{sec:mssm_combination_2015}
The results from the search for \AHtotautau on a
dataset corresponding to an integrated luminosity of 2.3 fb$^{-1}$
collected at a centre-of-mass energy of 13 TeV during 2015 are presented
in this section. As for the analysis discussed earlier
in the chapter a shape analysis is performed, however a different
discriminating variable, the transverse component of the di-$\Pgt$ mass
as reconstructed using the SVFit algorithm, was used. This variable
is denoted $m_{\text{T,\Pgt\Pgt}}$. The transverse di-$\Pgt$ mass 
distributions for the four channels are shown in figures \ref{fig:mssm_hig16006_mtsv_mt} -- \ref{fig:mssm_hig16006_mtsv_em}.
\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
\end{center}
\caption{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
observed events in the (a) no b-tag and (b) b-tag categories of the \mutau channel.
The signal overlaid corresponds to the signal of the three Higgs bosons at \mA=1 TeV and \tanb=50
in the $m_{\text{h}}^{\text{mod+}}$ scenario, and so it peaks once at low mass, for the light Higgs boson,
and once at higher mass, for the heavy H and A.}
\label{fig:mssm_hig16006_mtsv_mt}
\end{figure}

@@

\subsection{Combination procedure}
\label{sec:mssm_combination_procedure}
The idea of combining the two analyses is to combine the 
individual likelihoods to improve the analysis sensitivity and
physics reach. To do this correctly the correlations between
nuisance parameters in 2015 and 2016 need to be taken into account.
%Strictly, studies into the underlying correlations between
%nuisance parameters should be performed. This is however not always
%feasible and in some cases
The correlation scheme between nuisance parameters relating to the 2015 and 2016
analyses, as used for this combination, is given in table \ref{tab:mssm_combination_correlations}.

@@

To get a better idea of which analysis
is driving the sensitivity of the combination, we should consider the comparison
of expected limits in figure \ref{fig:mssm_results_combination_limits_comp}. The
gluon-fusion limits in figure \ref{fig:mssm_results_combination_limits_comp}a show that at
higher masses the analysis sensitivity is only very slightly improved with respect to the 
analysis of the 12.9 fb$^{-1}$ dataset. However, for masses between 200 and 800 GeV
there is a larger improvement in analysis sensitivity from combining the two analyses.
This is expected since the analysis on the 2016 dataset used a slightly different
selection that made the analysis more optimal at masses above 800 GeV,
and slightly less optimal below this mass, than the analysis on the 2015 dataset. This
effect is less visible on the b--associated production limits shown in figure \ref{fig:mssm_results_combination_limits_comp}b.

>>>>

In this chapter the search for neutral Higgs bosons \PHiggs or \PHiggsps
decaying to a pair of \Pgt leptons will be discussed. The results presented
here correspond to those from an analysis peformed on 12.9 fb$^{-1}$ collected
at $\sqrt{s}=13$ TeV during the first half of the 2016 p--p running period of the \ac{LHC}, 
detailed in reference \cite{CMS-PAS-HIG-16-037}. The \etau, \mutau, \tautau and \emu final
states of the di-\Pgt pair were studied. The results of this search are 
model--independent upper limits on $\sigma \times$ BR of \PHiggs or \PHiggsps 
production in the two modes (see THEORY) and decay into $\Pgt\Pgt$. The gluon fusion
production mode will also be referred to as gg$\phi$, and the b-associated production
mode will be referred to as bb$\phi$. In 
addition to the upper limits on cross--section times branching ratio of these two processes, 
the results are interpreted in MSSM benchmark scenarios and 2D likelihood
scans of the two production modes are performed. A very similar analysis
was performed on 2.3 fb$^{-1}$ of data collected at $\sqrt{s}=13$ TeV during the 2015 \ac{LHC} p--p running period. 
As it is so similar to the analysis performed on the 2016 dataset it
will not be described in detail here, more information can be found in reference \cite{CMS-PAS-HIG-16-006}.

For the analysis described in this chapter, as well as the 2015 analysis not detailed
here, I was responsible for all stages of the analysis. This includes optimisation of object selection and categorisation,
as well as studies of background methods for the \mutau, \etau and \tautau channels,
evaluation of systematic uncertainties in all four channels, and for producing
the statistical results, including model--dependent interpretations.

@@

\ttbar- and single-top background samples are generated using \texttt{Powheg},
with \texttt{MadGraph5\_aMC\@NLO} \cite{amcnlo} used for the generation of di--boson background
samples and part of the W+$\gamma$ background included in the \emu channel only.
\Wjets and \Zll backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
matrix element generator. Both samples containing a mixture
of jet multiplicities (`inclusive' samples) and samples with 1,2,3 or 4 jets (`exclusive' samples)
are generated. These exclusive samples increase the available number of
background events with higher jet multiplicities. %note LO samples used because to get same number of effective
%events would need to generate more NLO samples
The `inclusive' and `exclusive' samples are reweighted
before they are combined so as to preserve the correct
fractions of events with each jet multiplicity.
\texttt{MadGraph 5} 
is also used to generate part of the W+$\gamma$ background
samples.

@@

The selection was then optimised for mass points of around 1 TeV to obtain a combination
of the use of the medium hadronic tau isolation working point and a selection on \mT$<40$ GeV.

@@

The offline event selection continues by requiring both hadronic taus to be oppositely charged, separated
by $\Delta R > 0.5$, have pT~ of at least 40 GeV and $|\eta|<2.1$. Both taus need
to pass decay mode finding and have originated from the primary vertex, with the impact parameter $d_{z} < 0.2$ cm. 
Both taus need to pass the tight working point of the isolation discriminator, the very loose 
working point of the anti--electron discriminator and the loose working point of the anti--muon discriminator. 
The tight working point of the isolation discriminator is chosen to optimise the sensitivity
of this channel for higher masses, while retaining the second best senstivity in the intermediate
mass range, as seen in figure \ref{fig:mssm_tauid_tt}.
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./MSSM/Figures/ggh_tt_isolation.png}
\end{center}
\caption{Expected upper limits for gg$\phi$ process in the \tautau channel, using the 
loose (green), medium (red), tight (blue, very tight (black) and very very tight (gold)
working point. REMAKE?}
\label{fig:mssm_tauid_tt}
\end{figure}

@@

\chapter{Combination of MSSM analyses}
\label{sec:mssm_combination}
The results of the search for MSSM \AHtotautau on a dataset
corresponding to an integrated luminosity of 12.9 fb$^{-1}$, collected during the
first half of 2016 and thus referred to as `2016 analysis', can be combined 
with a previous search. This previous analysis, very similar to the 2016 analysis,
was performed on a dataset corresponding to an integrated luminosity of 2.3 fb$^{-1}$
collected during 2015 (`2015 analysis'), detailed in reference \cite{CMS-PAS-HIG-16-006}.
By combining the two analyses we should be able to set the most stringent
limits on the two MSSM production modes, and in the \mA-\tanb~ plane of 
MSSM benchmark scenarios, available at the time of writing. It is also
a first step on the way to combining the \AHtotautau analysis with
searches for charged Higgs bosons or heavy neutral Higgs bosons in 
other final states.

Because the 2015 analysis is very similar to the 2016 analysis it 
is not described in detail, however, the results will
be presented, and key differences with the more recent result highlighted
where needed.

\section{Results from 2015 analysis}
\label{sec:mssm_combination_2015}
The results from the search for \AHtotautau on a
dataset corresponding to an integrated luminosity of 2.3 fb$^{-1}$
collected at a centre-of-mass energy of 13 TeV during 2015 are presented
in this section. As for the analysis discussed earlier
in the chapter a shape analysis is performed, however a different
discriminating variable, the transverse component of the di-$\Pgt$ mass
as reconstructed using the SVFit algorithm, was used. This variable
is denoted $m_{\text{T,\Pgt\Pgt}}$. The transverse di-$\Pgt$ mass 
distributions for the four channels are shown in figures \ref{fig:mssm_hig16006_mtsv_mt} -- \ref{fig:mssm_hig16006_mtsv_em}.
\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_8_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_mt_9_hig16006_shapeshig16006_postfit_logy_logx.pdf}}
\end{center}
\caption{Transverse component of the di-$\Pgt$ mass for expected backgrounds and
observed events in the (a) no b-tag and (b) b-tag categories of the \mutau channel.
The signal overlaid corresponds to the signal of the three Higgs bosons at \mA=1 TeV and \tanb=50
in the $m_{\text{h}}^{\text{mod+}}$ scenario, and so it peaks once at low mass, for the light Higgs boson,
and once at higher mass, for the heavy H and A.}
\label{fig:mssm_hig16006_mtsv_mt}
\end{figure}

@@

\section{Combination procedure}
\label{sec:mssm_combination_procedure}
The idea of combining the two analyses is to combine the 
individual likelihoods to improve the analysis sensitivity and
physics reach. To do this correctly the correlations between
nuisance parameters in the 2015 and 2016 analyses need to be taken into account.
The only truly correct way to establish the correlations is to perform
dedicated studies into them. In many cases such studies would be 
unfeasible to perform, or it would not be clear how to approach the 
problem in the first place.

Even without performing such studies, a good estimate of what the correlation
should be can usually be based on reasoning. With a small number of 
exceptions this is what has been done for this combination.
%Strictly, studies into the underlying correlations between
%nuisance parameters should be performed. This is however not always
%feasible and in some cases
The correlation scheme between nuisance parameters relating to the 2015 and 2016
analyses, as used for this combination, is given in table \ref{tab:mssm_combination_correlations}. 
The third column gives the motivation for the chosen correlation.

@@

To get a better picture of how the sensitivity of the individual analyses compares
with the combination, we should consider the comparison
of expected limits in figure \ref{fig:mssm_results_combination_limits_comp}. The
gluon-fusion limits in figure \ref{fig:mssm_results_combination_limits_comp}a show that at
higher masses the analysis sensitivity is only very slightly improved with respect to the 
analysis of the 12.9 fb$^{-1}$ dataset. However, for masses between 200 and 800 GeV
there is a larger improvement in analysis sensitivity from combining the two analyses.
This behaviour is expected since the analysis on the 2016 dataset used a slightly different
selection that made the analysis more optimal at masses above 800 GeV,
and slightly less optimal below this mass, than the analysis on the 2015 dataset. This
effect is less visible on the b--associated production limits shown in figure \ref{fig:mssm_results_combination_limits_comp}b.
